---
title: "Documented Testing"
date: "12/4/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Testing of Cache Matrix

The testing of cache matrix was done with two different matrices, which we'll
call **inverseMatrix1** and **inverseMatrix2**, that we know are invertible.

```{r testing}
source("cachematrix.R")
inverseMatrix <- matrix(c(2, -1, 0, 1, 2, 1, 3, 4, 3), nrow=3, ncol=3)
inverseMatrix2 <- matrix(c(2,1,0,3,-1,1,1,2,0), nrow=3, ncol=3)
```

Then we'll create the helper vector that saves our matrices. 
```{r testing2}
helper <- makeCacheMatrix(inverseMatrix)
helper2 <- makeCacheMatrix(inverseMatrix2)
```

Finally, we call the cacheSolve function more than once per helper vector.

```{r testing3}
cacheSolve(helper)
cacheSolve(helper)
cacheSolve(helper2)
cacheSolve(helper2)
cacheSolve(helper)
```

We can see that the second and third time we run cache solve for each helper,
we return the cached one.

```{r testing4}
helper$set(inverseMatrix2)
cacheSolve(helper)
cacheSolve(helper)
```

If we set the helper for other function, the cache cleans, and it calculates
again the cached inverse.